Repeatability Test

### 2018-09-19 pt_characterization/rep_check/res2.tex
TODOs done

>>>>

\clearpage
\newpage

\subsubsection{Analysis on Some Outliers Found from INC16 and INC64 on {\tt sodb9}}
In this section we investigate what happened about some outlying samples on INC16 and INC64 
shown in Figures~\ref{fig:inc16_r2_hist_v5} and~\ref{fig:inc64_r2_hist_v5}.

%Regarding INC16, we looked into detailed information of processes that were 
%captured at some executions corresponding to the two bins of 16,041 (frequency = 3) 
%and 16,050 (frequency = 1) msecs in PT. 
Regarding INC16, we looked into detailed information of processes that were 
captured at one execution corresponding to the bin of 16,050 (frequency = 1) msec in PT. 
For the purpose of comparison, we also explored processes captured 
at the second-highest bin of 16,041 msec in PT.

Table~\ref{tab:inc16_daemons} shows the overall information of the captured processes at the two bins. 
As indicated by the table, there were 
some infrequent daemon processes such as {\tt sshd}, {\tt grep}, {\tt md0\_raid1}, {\tt cifsd}, running for some time 
when the INC16 program was run.

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|l|l|l|} \hline
Iteration number &  Process ID & Process Name  & PT (in msec)\\ \hline
77 (, 209, or 569) & 10185 & {\tt incr\_work} (=INC16) & 16,041 \\ \hline
& 28525 & {\tt proc\_monitor} & 196 \\ \hline
& 167 & {\tt kslowd001} &  1 \\ \hline
& 166 & {\tt kslowd000} &  1 \\ \hline \hline 
703 & 10185 & {\tt incr\_work} (=INC16) & 16,050 \\ \hline
& 28525 & {\tt proc\_monitor} & 196 \\ \hline
& 12322 & {\tt sshd} & 14 \\ \hline
& 12313 & {\tt sshd}  & 13 \\ \hline
& 12324 & {\tt grep}  &  6 \\ \hline
& 472 & {\tt md0\_raid1} &  2 \\ \hline
& 12314 & {\tt sshd}  &  2 \\ \hline
& 12315 & {\tt grep}  &  2 \\ \hline
& 12319 & {\tt grep}  &  1 \\ \hline
& 167 & {\tt kslowd001} &  1 \\ \hline
& 12323 & {\tt sshd}  &  1 \\ \hline
& 166 & {\tt kslowd000} &  1 \\ \hline
& 12328 & {\tt grep}  &  1 \\ \hline
& 1925 & {\tt cifsd} &  1 \\ \hline 
\hline
\end{tabular}
\end{center}
\caption{Daemons observed at the second-rightmost and rightmost bins in Figure~\ref{fig:inc16_r2_hist_v5}~\label{tab:inc16_daemons}}
\end{table}

Regarding INC64, we looked into detailed information of processes that were 
captured at one execution corresponding to the bin of 64,151 (frequency = 1) msec in PT. 
For the purpose of comparison, we also explored processes captured 
at the second-highest bin of 16,041 msec in PT.

Table~\ref{tab:inc64_daemons} shows the overall information of the captured processes at the two bins. 
As indicated by the table, there were also 
the same kind of infrequent daemon processes such as {\tt sshd}, {\tt grep}, {\tt md0\_raid1} as well as 
{\tt java} running for some time when the INC64 program was run. 
%In particular, we may not able to avoid hosting java for the longer INCs 
%as it appears by all means java ran due to any reason including GC 
%during such INCs' execution for some time. 
It is conjectured that for a longer INC program, it is more frequent to have {\tt java} with some positive time in PT.

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|l|l|l|} \hline
Iteration number &  Process ID & Process Name  & PT (in msec)\\ \hline
795 (, 125, or 236) & 16256 & {\tt incr\_work} (=INC64) & 16,142 \\ \hline
	& 28525 & {\tt proc\_monitor} & 198 \\ \hline
	& 167 & {\tt kslowd001} &  4 \\ \hline
	& 166 & {\tt kslowd000} &  3 \\ \hline 
(125) & (472) & ({\tt md0\_raid1}) & (2) \\ \hline
    & 16246 & {\tt java} &  2 \\ \hline 
\hline 
759 & 16256 & {\tt incr\_work} (=INC64) & 64,151 \\ \hline
& 28525 & {\tt proc\_monitor} & 198 \\ \hline
& 19320 & {\tt sshd} & 13 \\ \hline
& 19329 & {\tt sshd}  & 12 \\ \hline
& 19331 & {\tt grep}  &  5 \\ \hline
& 19322 & {\tt grep}  &  5 \\ \hline
& 167 & {\tt kslowd001} & 3\\ \hline
& 166 & {\tt kslowd000} &  3 \\ \hline
& 16246 & {\tt java} &  2 \\ \hline
& 2067 & {\tt sshd}  &  2 \\ \hline
& 19335 & {\tt grep}  &  1 \\ \hline
& 19330 & {\tt sshd}  &  1 \\ \hline
& 472 & {\tt md0\_raid1} &  1 \\ \hline
& 19326 & {\tt grep}  &  1 \\ \hline
\hline
\end{tabular}
\end{center}
\caption{Daemons observed at the second-rightmost and rightmost bins in Figure~\ref{fig:inc64_r2_hist_v5}~\label{tab:inc64_daemons}}
\end{table}

\clearpage
\newpage
